### 2021-03-29 Chapter-3/Chapter-3.tex
Updates from Overleaf

>>>>

CPUs can process data much faster than the main memory (DRAM) can supply it. To bridge the performance gap between the CPUs and the main memory, modern CPUs adopt a hierarchy memory. By storing extra copies of data and code in a smaller but faster memory, the software can get its most recently accessed code and data in a shorter time.

Figure~\ref{fig:memory_hierarchy} shows the overview of the hierarchy memory.

\begin{figure}
    \centering
    \includegraphics[width=.65\columnwidth]{./figures/chapter3/architecture.pdf}
    \caption{Computer Memory Hierarchy}\label{fig:memory_hierarchy}
\end{figure}
